Template Master's Thesis

### 2023-08-18 paper.tex
Update discussion

Address clustering through node embedding methods proved to be the most effective approach in our analysis. Unlike methods that require participation in specific on-chain events, node embedding examines the entire interaction network between addresses, making it broadly applicable. \newline
Our implementation of node embedding methods differs from previous approaches by \cite{Beres2020} and \cite{wu2022tutela}. We construct the network graph based on asset transfers between addresses of our predefined set and analyze on-chain data from two distinct blockchain networks: Polygon and Ethereum.

The main reasons for this are the different clustering objectives of previous implementations. \cite{wu2022tutela} aimed to cluster addresses without a predefined set, therefore using transaction data for network graph construction. Conversely, \cite{Beres2020} try to match deposit and withdrawal addresses for Tornado Cash, relying on all token transfers and transactions to cluster addresses based on similar on-chain behavior. Since it is not likely that withdrawal and deposit addresses from Tornado cash interacted with each other, the approach chosen by \cite{Beres2020} is better suited for that specific case.\newline
We validated our approach using ENS address pairs as ground truth and found better results in terms of average rank, when building the network graph out of intra-set asset transfers compared to using all token transfer events or transactions. \newline
Subsequently, we applied three node embedding algorithms that showed strong performance in the experiments of Beres et al. and compared their effectiveness. Our results indicate that Role2Vec is the best-performing method, locating the ground truth pair within the five nearest neighbors in 70\% of cases. This contrasts with Beres's findings, which identified Diff2Vec as the best method. \newline
However, determining why one approach outperforms another is challenging. Both Diff2Vec and DeepWalk preserve neighborhood characteristics, while Role2Vec is a structural node embedding method. % expand on structural node embedding and give possible explanation
Nevertheless, given the small sample size and the overall strong performance of all methods, the differences in results might be specific to the data at hand.

Wir haben eine eigene Methode entwickelt zum Clustern von Network embeddings.
Wir bauen Clusters abhängig von Euclidischer distanz zwischen feature vectors von nodes. 
Dazu benutzen wir die embeddings von role2vec.
Clusters aber sehr abhängig von threshold oder der methode wie man sie bildet, möglichkeit wäre weitere information (time-of-day) mit einfliessen zu lassen (evtl. sogar in den vector einbauen) -> wir haben es getestet aber kein (signifikantes) improvement für unsere address pairs gefunden. Könnte aber auch sein dass wir es falsch angewendet haben.

%und Beres hat ein kleineres Set an addressen (er will nur deposit und withdraw addressen von tornado cash clustern) und benutzt all token transfers und transaktionen, nicht nur diese zwischen den addressen, was bei ihm auch nicht viele wären da er es mit tornado anschaut und es nicht sinnvoll wäre zwischen den addressen zu interagieren.
%Im Gegensatz zu früheren implementierungen haben wir intra-set asset transfers benutzt um den graph zu bilden. das ist so weil bei unser spezifischen aufgabe ein vordefiniertes grosses addressen set zu clustern dies besser gelingt als bspw. alle transaktionen im ethereum netzwerk anzuschauen wie tutela oder wie beres der einfach alle token transfers der withdrawal und deposit addressen von tornado cash anschaut, wo sie eher weniger interaktionen haben als bei uns.
%Node embeddings mussten wir an unsere Gegebenheiten anpassen. Evaluierung mittels unsern ENS address paaren, hat gezeigt dass diese methode sehr gut funktioniert um ähnliche addressen zu finden.
%Despite the findings of \cite{Beres2020}, it appears that Diff2Vec is slightly less effective than Role2Vec or DeepWalk, although it is still generally successful. 
%Schwierig zu sagen wieso der eine Appraoch besser ist als der andere, der unterschied zwischen r2v und den anderen zwei ist das r2v ein role-based algorithmus ist und dies für unser spezielles datenset und unsere ENS address pairs besser zu funktionieren scheint. Aber nicht sehr aussagekräftig da kleines sample und alle approaches recht gut.
%%%%%%%%%%%%%%%%%%%%%

>>>>

Address clustering through node embedding methods proved to be the most effective approach in our analysis. Unlike methods that require participation in specific on-chain events, node embedding examines the entire interaction network between addresses, making it broadly applicable. Our implementation of node embedding methods differs from previous approaches by \cite{Beres2020} and \cite{wu2022tutela}. We construct the network graph based on asset transfers between addresses of our predefined set and analyze on-chain data from two distinct blockchain networks: Polygon and Ethereum. \newline
The main reasons for this are the different clustering objectives of previous implementations. \cite{wu2022tutela} aimed to cluster addresses without a predefined set, therefore using transaction data for network graph construction. Conversely, \cite{Beres2020} try to match deposit and withdrawal addresses for Tornado Cash, relying on all token transfers and transactions to cluster addresses based on similar on-chain behavior. Since it is not likely that withdrawal and deposit addresses from Tornado cash interacted with each other, the approach chosen by \cite{Beres2020} is better suited for that specific case.\newline
We validated our approach using ENS address pairs as ground truth and found better results in terms of average rank, when building the network graph out of intra-set asset transfers compared to using all token transfer events or transactions. \newline
Subsequently, we applied three node embedding algorithms that showed strong performance in the experiments of \cite{Beres2020} and compared their effectiveness. Our results indicate that Role2Vec is the best-performing method, locating the ground truth pair within the five nearest neighbors in 70\% of cases. This contrasts with previous findings, which identified Diff2Vec as the most effective method. \newline
Determining why one approach outperforms another is challenging. Both Diff2Vec and DeepWalk preserve neighborhood characteristics, while Role2Vec is a structural node embedding method, meaning that ... A possible explanation is that Role2Vec ... % expand on structural node embedding and give possible explanation
Nevertheless, given the small sample size and the overall strong performance of all methods, the differences in results might be specific to the data at hand. \newline
We devised a novel method for creating clusters from our node embeddings, enabling us to estimate the number of entities represented by the 51,566 network graph nodes/addresses. This method involved calculating the Euclidean distance between pairs of feature vectors, specifically using the node embedding matrix generated by Role2Vec. Nodes were clustered if their distance fell below a predetermined threshold, and any overlapping clusters were subsequently merged. \newline
Though our method may not be the ideal approach for clustering, it is likely more effective than simply clustering a fixed number of $k$ addresses. We observed that the number of clusters and their size is highly sensitive to the chosen distance threshold, making it challenging to assess the accuracy of these clusters. We have provided a sensitivity analysis to illustrate this issue. The distances between the feature vectors tend to be quite narrow (dense vectors), and even the distances between ground truth pairs exhibit significant variation. \newline
We explored potential enhancements to our method, such as incorporating additional information (e.g., Time of Day, normalized Gas) into the feature vectors. Unfortunately, these modifications did not yield improvements. Similarly, a two-step approach to clustering also proved unsuccessful. These areas remain open for future research.

%Clusters aber sehr abhängig von threshold oder der methode wie man sie bildet, möglichkeit wäre weitere information (time-of-day) mit einfliessen zu lassen (evtl. sogar in den vector einbauen) -> wir haben es getestet aber kein (signifikantes) improvement für unsere address pairs gefunden. Könnte aber auch sein dass wir es falsch angewendet haben.
%und Beres hat ein kleineres Set an addressen (er will nur deposit und withdraw addressen von tornado cash clustern) und benutzt all token transfers und transaktionen, nicht nur diese zwischen den addressen, was bei ihm auch nicht viele wären da er es mit tornado anschaut und es nicht sinnvoll wäre zwischen den addressen zu interagieren.
%Im Gegensatz zu früheren implementierungen haben wir intra-set asset transfers benutzt um den graph zu bilden. das ist so weil bei unser spezifischen aufgabe ein vordefiniertes grosses addressen set zu clustern dies besser gelingt als bspw. alle transaktionen im ethereum netzwerk anzuschauen wie tutela oder wie beres der einfach alle token transfers der withdrawal und deposit addressen von tornado cash anschaut, wo sie eher weniger interaktionen haben als bei uns.
%Node embeddings mussten wir an unsere Gegebenheiten anpassen. Evaluierung mittels unsern ENS address paaren, hat gezeigt dass diese methode sehr gut funktioniert um ähnliche addressen zu finden.
%Despite the findings of \cite{Beres2020}, it appears that Diff2Vec is slightly less effective than Role2Vec or DeepWalk, although it is still generally successful. 
%Schwierig zu sagen wieso der eine Appraoch besser ist als der andere, der unterschied zwischen r2v und den anderen zwei ist das r2v ein role-based algorithmus ist und dies für unser spezielles datenset und unsere ENS address pairs besser zu funktionieren scheint. Aber nicht sehr aussagekräftig da kleines sample und alle approaches recht gut.
%%%%%%%%%%%%%%%%%%%%%
